A Partitioning Algorithm for Maximum Common Subgraph Problems

### 2017-02-16 paper/paper.tex
Spelling
Promise URL for code

Experiments were performed on machines with dual Intel Xeon E5-2640 v2 CPUs and
64GBytes RAM. Our algorithm was implemented in C++ and compiled using g++
5.3.0. For comparison, we compare against the best constraint programming
implementations of \citet{DBLP:conf/cp/NdiayeS11} and
\citet{DBLP:conf/cp/McCreeshNPS16} (CP-FC in the unlabelled cases, and CP-MAC
in the labelled cases, using both branching and filtering for connected
subgraphs), the clique encodings of \citet{DBLP:conf/cp/McCreeshNPS16}, and the
$k\downarrow$ algorithm of \citet{UpcomingAAAIPaper} (which only supports
unlabelled, undirected, unconnected instances).

@@

Why is this? We do not see a similar correlation between our search space size
and that of the clique spproach. The key observation is that \McSplit\ may be
considered to be a different version of the constraint CP-FC algorithm, using
an unconventional domain store and more efficient filtering algorithms. We now
explore this relationship further.

>>>>

Experiments were performed on machines with dual Intel Xeon E5-2640 v2 CPUs and
64GBytes RAM. Our algorithm was implemented\footnote{URL removed for anonymous
review} in C++ and compiled using g++ 5.3.0. For comparison, we compare against
the best constraint programming implementations of
\citet{DBLP:conf/cp/NdiayeS11} and \citet{DBLP:conf/cp/McCreeshNPS16} (CP-FC in
the unlabelled cases, and CP-MAC in the labelled cases, using both branching
and filtering for connected subgraphs), the clique encodings of
\citet{DBLP:conf/cp/McCreeshNPS16}, and the $k\downarrow$ algorithm of
\citet{UpcomingAAAIPaper} (which only supports unlabelled, undirected,
unconnected instances).

@@

Why is this? We do not see a similar correlation between our search space size
and that of the clique approach. The key observation is that \McSplit\ may be
considered to be a different version of the constraint CP-FC algorithm, using
an unconventional domain store and more efficient filtering algorithms. We now
explore this relationship further.
